---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# ShinyRating

<!-- ex : https://metroui.org.ua/rating.html -->
<!-- ex : https://www.wbotelhos.com/raty -->
<!-- https://github.com/Monte9/react-native-ratings -->

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!--[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://cran.r-project.org/web/licenses/MIT)-->
[![R-CMD-check](https://github.com/mhanf/ShinyRating/workflows/R-CMD-check/badge.svg)](https://github.com/mhanf/ShinyRating/actions)
[![License: GPLv3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://opensource.org/licenses/GPL-3.0)
[![CRAN status](https://www.r-pkg.org/badges/version/ShinyRating)](https://CRAN.R-project.org/package=ShinyRating)
<!-- badges: end -->

Easy creation of rating widgets in Shiny.

## Features

* Optimized for [Bootstrap 5](https://getbootstrap.com/) 
* possibility to use [fontawesome 6.1.2](https://fontawesome.com/icons) icons as user-defined SVG images
* Simple definition of the number, size (height and width), type, color and animation of icons
* Possibility to add tooltips
* Read only, hover and accumulation modes
* Possibility to define individual setting rules for icons
* Compatible with server validation of inputs based on [shinyvalidate](https://rstudio.github.io/shinyvalidate) package

## Installation

You can install the development version of ShinyRating from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mhanf/ShinyRating")
```
## Example

ShinyRating exports two main functions: `ratingInput()` and `updateRatingInput()`. 

A Shiny app example using these functions can be created as follows:

``` {r installation, eval=FALSE}
# libraries
library(shiny)
library(ShinyRating)
library(bslib)
# ui part
ui <- function(){
  fluidPage(
    theme = bslib::bs_theme(
      version = 5,
      bootswatch = "flatly"
    ),
    br(),
    fluidRow(
      column(
        width = 12,
        align = "center",
        br(),
        ratingInput(
          inputId = "Mood",
          label = "How do you feel ?",
          number = 5,
          value = NA,
          cumul = FALSE,
          hover = TRUE,
          i_width = "2em",
          i_height = "2em",
          on_color = c("danger","warning","dark","info","success"),
          off_color = "light",
          i_name = c("face-angry","face-frown","face-meh","face-smile","face-laugh"),
          i_lib = "fontawesome",
          anim = "pulse",
          duration = 1,
          tlp = TRUE,
          tlp_color = c("danger","warning","dark","info","success"),
          tlp_position = "bottom",
          tlp_msg = c("Angry","Frown","Neutral","Happy","Excited")
        ),
        br(),
        ratingInput(
          inputId = "star",
          label = "Where is shinyRating on the fun scale ?",
          anim = "tada",
          i_width = "2em",
          i_name = "star",
          i_lib = "fontawesome",
          on_color = "#D5AB55",
          cumul = TRUE,
          hover = TRUE
        ),
        br(),
        ratingInput(
          inputId = "animal",
          label = "What is your favorite animal ?",
          i_width = "2.5em",
          i_name = c("cow","hippo","otter","cat","dog"),
          anim = "heartBeat",
          off_color = "black",
          tlp = TRUE,
          tlp_msg = c("Cow","Hippo","Otter","Cat","Dog")
        ),
        br(),
        actionButton("go","Reset",class="btn-success m-1")
      )
    )
  )
}
# Server part
server <- function(input, output, session) {
  observeEvent( 
    input$go , {
      updateRatingInput(session, "star")
      updateRatingInput(session, "Mood", value = 3)
      updateRatingInput(session, "animal")
    }
  )
  #observe({print(input$Mood)})
}
# launch the app
shinyApp(ui = ui, server = server)
```

You can run a gallery with :

```{r example, eval=FALSE}
ShinyRating::app_gallery()
```

## Prior art & philosophy

The core functionnalities of this package are similar to those of the [ShinyRatingInput](https://github.com/stefanwilhelm/ShinyRatingInput). This package tries to overcome some limitations by being compatible with the shinyverse packages developed by Rstudio (mostly [shinyvalidate](https://rstudio.github.io/shinyvalidate/) [bslib](https://rstudio.github.io/bslib/)) and [fontawesome](https://github.com/rstudio/fontawesome) as well as extending its functionnalities (color, size, animation ...). The tooltip functionality is inspired from the one of the [bsutils](https://github.com/JohnCoene/bsutils) package. SVG loading functionnalities are strongly inspired from the ones of [icons](https://github.com/mitchelloharawild/icons) package.The idea to use [animate.css](https://animate.style/) comes from the [shinyanimate](https://github.com/Swechhya/shinyanimate) package.

## Contributions

The developer and maintainer is [mhanf](https://github.com/mhanf). External contributions are welcome. Please keep in mind that I am not a professional R developer but an enthusiastic R data scientist who plays with shiny and javascript as a pretext to learn new stuffs. Unfortunately, so is my code. Please note that the ShinyRating project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

## License

The ShinyRating package as a whole is licensed under the [GPLv3](https://www.fsf.org/) license.The animate.css library used in this package is licensed under the [HL3](https://firstdonoharm.dev/) license.
